### 2019-01-02 revisions/review-responses.tex

        %---------------------------------------------------------------------

        \question The most critical point of the work is that the built-in 
        capabilities for online reprocessing of Serpent 2 have not been used. 
        Their use is mentioned in the future work, but it is not clear why 
        these capabilities have not been used in the current work. To the 
        author's knowledge, they have been available in Serpent 2 since quite a 
        while. The authors should clarify this point at the beginning of the 
        paper, and not only in the ``Future work'' section. Even though the 
        technical work was done without using these capabilities, they should 
        highlight what  SaltProc adds to the built-in Serpent capabilities, and 
        they should at least try to extrapolate on the potential advantages of 
        combining  SaltProc and Serpent capabilities. Based on this, they 
        should slightly restructure the paper in order to prove the claimed 
        advantages over Serpent 2.
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question Considering the scope of the journal, mentioning the names of 
        companies and start-up is not appropriate. I would suggest removing 
        them.
        \begin{solution}
                The names of companies have been removed.
        \end{solution}

@@

        %---------------------------------------------------------------------

        \question The sentence ``Immediate advantages over traditional, solid-fueled, 
        reactors include near-atmospheric pressure in the 15 primary loop, 
        relatively high coolant temperature, outstanding neutron economy, 
        improved safety parameters,'' may suggest improved neutron economy vs 
        solid-fuel fast reactors. This is rarely the case, especially vs 
        Pu-based SFRs. I would suggest reformulating.
        \begin{solution}
                Thank you for the exceptional recommendation. The sentence has been 
                changed as follows:

                ``Immediate advantages over traditional light water reactors 
                include\dots''
        \end{solution}

@@

        %---------------------------------------------------------------------

        \question The sentence ``With regard to the nuclear fuel cycle, the 
        thorium cycle produces a reduced quantity of plutonium and minor 
        actinides (MAs) compared to the traditional uranium fuel cycle'' is 
        correct, but the fact that this is an advantage is questionable. The 
        pros\&cons of thorium cycle have been long debated and there is no 
        consensus on its advantage in terms of exposure of workers, exposure of 
        public, geological repository, etc. I would suggest removing the 
        sentence.
        \begin{solution}
                Thanks for your kind comment. The sentence has been removed.
        \end{solution}

        \question ``Methods listed in references [14, 17, 24, 25, 28, 29, 30] 
        as well as the current work also employ a batch-wise approach''. As a 
        matter of fact, the work in [14]  allows for continuous reprocessing 
        via introduction of ``reprocessing'' time constants. The work from  
        Aufiero (mentioned in the following paragraph) actually used the 
        methodology previously developed in [14]  for verification purposes.
        \begin{solution}
                Thank you for the information. [14] has been removed from the 
                sentence, and following paragraph has been modified to read:

                Accounting for continuous removal or addition presents a greater 
                challenge since it requires adding a term to the Bateman equations. 
                Fiorina \emph{et al.} simulated MSFR depletion with continuous
                 fuel salt reprocessing via introducing ``reprocessing'' time 
                constants into ERANOS transport code \cite{fiorina_investigation_2013}. 
                Aufiero \emph{et al.} improved SERPENT2 using similar methodology by 
                explicitly introducing continuous reprocessing in the system of Bateman 
                equations by adding effective decay and transmutation terms for the 
                different nuclides \cite{aufiero_extended_2013}. 
        \end{solution}

@@

        %---------------------------------------------------------------------

        \question Table 3. It is not clear what ``effective cycle times'' are. 
        Please clarify.
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question The removal of fission products is made batch wise in the 
        described algorithms. However it is not clear how the fission products 
        with the longest ``effective cycle times'' are removed. Part of them at 
        every batch? Or all of them at the end of the  ``effective cycle 
        times''.  Please clarify. And please clarify the relation between 
        ``effective cycle times'', batches and the average time spent by a 
        fission product in the reactor.
        \begin{solution}
                All of them at the end of the cycle time, and we agree that it
                 was not best solution. To clarify this following paragraph has 
                been added:

				Current version of SaltProc only allows separate out 100\% of 
				specific elements or group of elements (e.g. Processing Groups 
				as described in Table 3 at the end
				 of the specific cycle time. This approach works well for 
				fast-removing elements (gases, noble metals, protactinium) which 
				should be removed each depletion step. Unfortunately, for the 
				elements with longer cycle time (i.e. rare earths should be removed 
				every 50 days) this simplified approach leads to oscillatory 
				behavior of all major parameters. In future releases of SaltProc
				 this drawback will be eliminated by removing elements with longer 
				cycle times using different method: only mass fraction (calculated 
				separately for each reprocessing group) will be removed each 
				depletion step (e.g. 3 days).	
        \end{solution}

@@

        %---------------------------------------------------------------------

        \question The oscillatory behavior shown in Fig. 7 on the time scale of 
        months/years is hard to explain. Is this because the fission product 
        with longer residence time are batch-wise removed at their ``effective 
        cycle time''? In case, why not to remove part of them at every depletion 
        step?  
        \begin{solution}
                Yes, the oscillation happened because the fission products 
        		with longer residence time are removed at the end of cycle time. We are 
                definitely will take your advice and improve the code in future 
                releases. Following text has been added to clarify this issue:

                In fact, SaltProc fully removes all these elements every 3435 days 
                (not a small mass fraction every 3 days) which causes the 
                multiplication factor to jump by approximately 450 pcm, and limits 
                using the batch approach for online reprocessing simulations. In 
                future versions of SaltProc this drawback will be eliminated by 
                removing elements with longer residence time (seminoble metals, 
                volatile fluorides, Rb, Sr, Cs, Ba, Eu) using different approach. 
                Only mass fraction (calculated separately for each reprocessing 
                group) will be removed every depletion step (e.g. 3 days) instead 
                of removing 100\% of element atoms after cycle time.
        \end{solution}

@@

        %---------------------------------------------------------------------

        \question ``The fuel temperature coefficient (FTC) is negative for both 
        initial and equilibrium fuel compositions due to thermal Doppler 
        broadening of the resonance capture cross sections in the thorium.'' 
        What is the effect of density?
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question ``This thorium consumption rate is in good agreement with a 
        recent online reprocessing study by ORNL [29].'' Please notice that in a 
        reactor with only Th as feed, and near equilibrium, the Th consumption 
        rate is  exclusively determined by the reactor power and by the energy 
        released per fission.  
        \begin{solution}
                Thank you for the recommendation. Following sentence has been 
                added:

                It must be noted that for the reactor with only thorium feed, 
                at near equilibrium state, the thorium consumption rate is 
				determined by the reactor power, the energy released per fission, 
				and neutron energy spectrum.
        \end{solution}

@@

        %---------------------------------------------------------------------

        \question Are you considering the effect of the gradual poisoning of 
        the graphite with fission products? If not, it would be worthwhile 
        briefly discussing its effect.
        \begin{solution}
                This passage has been added:

				$^{135}$Xe is a strong poison to the reactor, and some 
				fraction of this gas is absorbed by graphite during \gls{MSBR} 
				operation. ORNL calculations shown that for unsealed commercial 
				graphite with helium permeability 10$^{-5}$ cm$^2$/s the 
				calculated poison fraction is less than 2\% \cite{robertson_conceptual_1971}. 
				This parameter can be improved by using experimental graphites 
				or by applying sealing technology. The effect of the gradual 
				poisoning of the core graphite with xenon is not treated here.
        \end{solution}

@@

        %---------------------------------------------------------------------

        \question In the manuscript it is not always clear when the authors 
        refer to numerical approximations of physical situations. For instance, 
        the authors write ``Figure 16 demonstrates that batch-wise removal of 
        strong absorbers every 3 days did not necessarily leads to fluctuation 
        in results but rare earth elements 480 removal every 50 days causes an 
        approximately 600 pcm jump in reactivity.'' These 600 pcm are an effect 
        of a numerical approximation, but the way things are presented can be 
        confusing to the reader. Please try to explicitly separate physical and 
        numerical effects. And try to related numerical effects to physical 
        effects. For instance, how does these numerical ``jumps'' affect the 
        results?  In this sense, why the batch-wise removal of strong absorbers 
        every 3 days  was not done? And why a fraction of rare earths  is not 
        removed every three days?
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question ``The current work results show that a true equilibrium 
        composition cannot exist but balance between strong absorber 
        accumulation and new fissile material production can be achieved to 
        keep the reactor critical.'' Not clear. Do you mean that the equilibrium 
        composition cannot be achieved in a lifetime of the reactor? Please 
        clarify
        \begin{solution}
                This statement has been removed completely.
        \end{solution}

### 2019-01-02 introduction.tex
Reviewer 2 minor comments mostly resolved #39

In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile 
materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic 
elements}F$_3$) combine with carrier salts to form a liquid fuel that 
circulates in a loop-type primary circuit \cite{haubenreich_experience_1970}. 
Immediate advantages over traditional, solid-fueled, reactors include 
near-atmospheric pressure in the primary loop, 
relatively high coolant temperature, outstanding neutron economy, improved 
safety parameters, reduced fuel preprocessing, and the ability to continuously 
remove fission products and add fissile and/or fertile elements 
\cite{leblanc_molten_2010}.

The thorium-fueled \gls{MSBR} was developed in the 
early 1970s by \gls{ORNL} specifically to explore the promise of the thorium 
fuel cycle, which uses natural thorium instead of enriched uranium. With 
continuous fuel reprocessing, the \gls{MSBR} realizes the advantages of the 
thorium fuel cycle because the $^{233}$U bred from 
$^{232}$Th is almost instantly\footnote{\space $^{232}$Th transmuted into 
$^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa 
($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U 
($\tau_{1/2}$=26.967d).} recycled back into the core 
\cite{betzler_modeling_2016}. The chosen fuel salt, LiF-BeF$_2$-ThF$_4$-UF$_4$, has a 
melting point of $499^\circ$C, a low vapor pressure at operating temperatures, 
and good flow and heat transfer properties \cite{robertson_conceptual_1971}. 
With regard to the nuclear fuel cycle, the thorium cycle produces a reduced quantity 
of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle. 
Finally, the \gls{MSR} also could be employed as a converter reactor for 
transmutation of spent fuel from current \glspl{LWR}.

@@

\begin{table}[ht!]
\caption{Tools and methods for fast spectrum system fuel cycle analysis.}
\begin{tabularx}{\textwidth}{ m | b | x } 
\hline Neutronic code    & \qquad Authors & Spectrum   \\
\hline
\gls{MCNP}/REM \cite{noauthor_mcnp_2004,heuer_simulation_2010}  & Doligez 
\emph{et al.}, 2014; Heuer \emph{et al.}, 2014  
\cite{doligez_coupled_2014,heuer_towards_2014}    & fast \\
\hline
ERANOS \cite{ruggieri_eranos_2006}  & Fiorina \emph{et al.}, 2013 
\cite{fiorina_investigation_2013}            & fast \\
\hline
KENO-IV/ORIGEN \cite{goluoglu_monte_2011,gauld_isotopic_2011}     & Sheu 
\emph{et al.}, 2013 \cite{sheu_depletion_2013} & fast \\
\hline
SERPENT 2 \cite{leppanen_serpent_2015}  & Aufiero \emph{et al.}, 2013 
\cite{aufiero_extended_2013} & fast \\
\hline
MCODE/ORIGEN2 \cite{xu_mcode_2008,croff_users_1980}      & Ahmad \emph{et al.}, 
2015 \cite{ahmad_neutronics_2015}   & thermal  \\
\hline
\gls{MCNP}6/CINDER90 \cite{goorley_mcnp6_2013}     & Park \emph{et al.}, 2015; 
Jeong \emph{et al.}, 2016 \cite{park_whole_2015, jeong_equilibrium_2016}& 
thermal\\
\hline
SCALE/TRITON \cite{bowman_scale_2011,powers_new_2013}    & Powers \emph{et al.}, 
2014; Betzler \emph{et al.}, 2017 
\cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal/fast\\
\hline
SERPENT 2     & Rykhlevskii \emph{et al.}, 2017 \cite{rykhlevskii_online_2017} & 
thermal\\
\hline
\gls{MCNP}/REM  & Nuttin \emph{et al.} \cite{nuttin_potential_2005}&thermal  \\ 
\hline
\end{tabularx}
  \label{tab:fs_codes}
\end{table}
\FloatBarrier

@@

Many liquid-fueled \gls{MSR} designs rely on online fuel processing in which  
material moves to and from the core continuously or at specific time steps 
(batch-wise). In the batch-wise approach, the burn-up simulation stops at a given 
time and restarts with a new liquid fuel composition (after removal of discarded 
materials and addition of fissile/fertile materials). \gls{ORNL} researchers 
have developed ChemTriton, a Python-based script for SCALE/TRITON which uses the 
batch-wise approach to simulate a continuous reprocessing and refill using a single 
or multiple unit cell. ChemTriton models salt 
treatment, separations, discharge, and refill using a unit-cell \gls{MSR} 
SCALE/TRITON depletion simulation over small time steps to simulate continuous 
reprocessing and deplete the fuel salt \cite{powers_new_2013}. Methods listed in 
references \cite{fiorina_investigation_2013,sheu_depletion_2013,park_whole_2015, 
jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} 
as well as the current work also employ a batch-wise approach.

Accounting for continuous removal or addition presents a greater challenge since it 
requires adding a term to the Bateman equations. Aufiero \emph{et al.} explicitly
introduced online fuel reprocessing in the system of equations by adding effective 
decay and transmutation terms for the different nuclides. The latest SCALE release will also have the same functionality using truly continuous removals \cite{betzler_implementation_2017}. In his work SERPENT was 
used for solution of the matrix exponential derived from the system of the Bateman 
equations \cite{aufiero_extended_2013}. Similar approach is adopted to model true 
continuous feeds and removals using MCNP transport code listed in references 
\cite{doligez_coupled_2014,heuer_towards_2014,nuttin_potential_2005}.

@@

The present work introduces the online reprocessing simulation package, SaltProc, 
which expands the capability of the continuous-energy Monte Carlo Burnup 
calculation code, SERPENT 2 \cite{leppanen_serpent_2015}, for simulation 
liquid-fueled \gls{MSR} operation 
\cite{rykhlevskii_arfc/saltproc:_2018}. It also reports the 
application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, an 
extension of the work presented in 
\cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. In this work, we 
analyzed \gls{MSBR} neutronics and fuel cycle to establish its equilibrium core 
composition. Additionally, we compared predicted operational and safety parameters of the \gls{MSBR} at 
both the initial and equilibrium states to characterize the evolution of its 
safety case over time. Finally, these simulations determined the appropriate $^{232}$Th feed rate  
for maintaining criticality and enabled analysis of the overall \gls{MSBR} fuel 
cycle performance.

>>>>

In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile 
materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic 
elements}F$_3$) combine with carrier salts to form a liquid fuel that 
circulates in a loop-type primary circuit \cite{haubenreich_experience_1970}. 
Immediate advantages over traditional light water reactors include 
near-atmospheric pressure in the primary loop, 
relatively high coolant temperature, outstanding neutron economy, improved 
safety parameters, reduced fuel preprocessing, and the ability to continuously 
remove fission products and add fissile and/or fertile elements 
\cite{leblanc_molten_2010}.

The thorium-fueled \gls{MSBR} was developed in the 
early 1970s by \gls{ORNL} specifically to explore the promise of the thorium 
fuel cycle, which uses natural thorium instead of enriched uranium. With 
continuous fuel reprocessing, the \gls{MSBR} realizes the advantages of the 
thorium fuel cycle because the $^{233}$U bred from 
$^{232}$Th is almost instantly\footnote{\space $^{232}$Th transmuted into 
$^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa 
($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U 
($\tau_{1/2}$=26.967d).} recycled back into the core 
\cite{betzler_modeling_2016}. The chosen fuel salt, LiF-BeF$_2$-ThF$_4$-UF$_4$, has a 
melting point of $499^\circ$C, a low vapor pressure at operating temperatures, 
and good flow and heat transfer properties \cite{robertson_conceptual_1971}.  
Finally, the \gls{MSR} also could be employed as a converter reactor for 
transmutation of spent fuel from current \glspl{LWR}.

@@

\begin{table}[ht!]
\caption{Tools and methods for fast spectrum system fuel cycle analysis.}
\begin{tabularx}{\textwidth}{ m | b | x } 
\hline Neutronic code    & \qquad Authors & Spectrum   \\
\hline
\gls{MCNP}/REM \cite{noauthor_mcnp_2004,heuer_simulation_2010}  & Doligez 
\emph{et al.}, 2014; Heuer \emph{et al.}, 2014  
\cite{doligez_coupled_2014,heuer_towards_2014}    & fast \\
\hline
ERANOS \cite{ruggieri_eranos_2006}  & Fiorina \emph{et al.}, 2013 
\cite{fiorina_investigation_2013}            & fast \\
\hline
KENO-IV/ORIGEN \cite{goluoglu_monte_2011,gauld_isotopic_2011}     & Sheu 
\emph{et al.}, 2013 \cite{sheu_depletion_2013} & fast \\
\hline
SERPENT 2 \cite{leppanen_serpent_2015-1}  & Aufiero \emph{et al.}, 2013 
\cite{aufiero_extended_2013} & fast \\
\hline
DIF3D \cite{derstine_dif3d:_1984} & Zhou \emph{et al.}, 2018 
\cite{zhou_fuel_2018} & thermal/ fast \\
\hline
MCODE/ORIGEN2 \cite{xu_mcode_2008,croff_users_1980}      & Ahmad \emph{et al.}, 
2015 \cite{ahmad_neutronics_2015}   & thermal  \\
\hline
\gls{MCNP}6/CINDER90 \cite{goorley_mcnp6_2013}     & Park \emph{et al.}, 2015; 
Jeong \emph{et al.}, 2016 \cite{park_whole_2015, jeong_equilibrium_2016}& 
thermal\\
\hline
SCALE/TRITON \cite{bowman_scale_2011,powers_new_2013}    & Powers \emph{et al.}, 
2014; Betzler \emph{et al.}, 2017 
\cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal\\
\hline
SERPENT 2     & Rykhlevskii \emph{et al.}, 2017 \cite{rykhlevskii_online_2017} & 
thermal\\
\hline
\gls{MCNP}/REM  & Nuttin \emph{et al.} \cite{nuttin_potential_2005}&thermal  \\ 
\hline
\end{tabularx}
  \label{tab:fs_codes}
\end{table}
\FloatBarrier

@@

Many liquid-fueled \gls{MSR} designs rely on online fuel processing in which  
material moves to and from the core continuously or at specific time steps 
(batch-wise). In the batch-wise approach, the burn-up simulation stops at a given 
time and restarts with a new liquid fuel composition (after removal of discarded 
materials and addition of fissile/fertile materials). \gls{ORNL} researchers 
have developed ChemTriton, a Python-based script for SCALE/TRITON which uses the 
batch-wise approach to simulate a continuous reprocessing. ChemTriton models salt 
treatment, separations, discharge, and refill using a unit-cell \gls{MSR} 
SCALE/TRITON depletion simulation over small time steps to simulate continuous 
reprocessing and deplete the fuel salt \cite{powers_new_2013}. Methods listed in 
references \cite{zhou_fuel_2018,sheu_depletion_2013,park_whole_2015, 
jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} 
as well as the current work also employ a batch-wise approach.

Accounting for continuous removal or addition presents a greater challenge since it 
requires adding a term to the Bateman equations. Fiorina \emph{et al.} simulated 
\gls{MSFR} depletion with continuous fuel salt reprocessing via introducing 
``reprocessing'' time constants into ERANOS transport code \cite{fiorina_investigation_2013}. Aufiero \emph{et al.} improved SERPENT2 using similar methodology by explicitly introducing 
continuous reprocessing in the system of Bateman equations by adding effective decay and transmutation terms for the different nuclides \cite{aufiero_extended_2013}.

The latest SCALE release will also have the same functionality using truly continuous removals \cite{betzler_implementation_2017}. In his work SERPENT was 
used for solution of the matrix exponential derived from the system of the Bateman 
equations \cite{aufiero_extended_2013}. Similar approach is adopted to model true 
continuous feeds and removals using MCNP transport code listed in references 
\cite{doligez_coupled_2014,heuer_towards_2014,nuttin_potential_2005}.

@@

The present work introduces the online reprocessing simulation package, SaltProc, 
which expands the capability of the continuous-energy Monte Carlo Burnup 
calculation code, SERPENT 2 \cite{leppanen_serpent_2015-1}, for simulation 
liquid-fueled \gls{MSR} operation 
\cite{andrei_rykhlevskii_arfc/saltproc:_2018}. It also reports the 
application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, an 
extension of the work presented in 
\cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. In this work, we 
analyzed \gls{MSBR} neutronics and fuel cycle to establish its equilibrium core 
composition. Additionally, we compared predicted operational and safety parameters of the \gls{MSBR} at 
both the initial and equilibrium states to characterize the evolution of its 
safety case over time. Finally, these simulations determined the appropriate $^{232}$Th feed rate  
for maintaining criticality and enabled analysis of the overall \gls{MSBR} fuel 
cycle performance.

### 2019-01-02 methods.tex
Reviewer 3 minor comments mostly resolved #35
Reviewer 2 minor comments mostly resolved #39

@@

>>>>

$^{135}$Xe is a strong poison to the reactor, and some fraction of this gas 
is absorbed by graphite during \gls{MSBR} operation. ORNL calculations shown 
that for unsealed commercial graphite with helium permeability 10$^{-5}$ cm$^2$/s 
the calculated poison fraction is less than 2\% \cite{robertson_conceptual_1971}. 
This parameter can be improved by using experimental graphites or by applying
sealing technology. The effect of the gradual poisoning of the core graphite 
with xenon is not treated here.
% Consequently, minimizing
% xenon absorption in a graphite is desirable. 
%ORNL calculations shown 
%that the graphite must have a gas permeability in the order of 10$^{-8}$ cm$^2$/s 
%to keep the xenon poisoning about 0.5\%. The best commercially available graphites 
%have this parameter in the range from 10$^{-3}$ to 10$^{-4}$ cm$^2$/s, hence, 
%desirable parameters ca be achieved only by sealing the graphite

@@

Current version of SaltProc only allows separate out 100\% of specific elements 
or group of elements (e.g. Processing Groups as described in 
Table~\ref{tab:reprocessing_list}) at the end of the specific cycle time. 
This approach works well for fast-removing elements (gases, noble metals, 
protactinium) which should be removed each depletion step. Unfortunately, 
for the elements with longer cycle time (i.e. rare earths should be removed 
every 50 days) this simplified approach leads to oscillatory behavior of all
major parameters. In future releases of SaltProc this drawback will be eliminated 
by removing elements with longer cycle times using different method: only mass 
fraction (calculated separately for each reprocessing group) will be removed each
 depletion step (e.g. 3 days).

### 2019-01-02 results.tex
Reviewer 2 minor comments mostly resolved #39

Additionally, the presence of rubidium, strontium, cesium, and barium in the 
core are disadvantageous to reactor physics. In fact, the removal of these elements 
every 3435 days causes the multiplication factor to jump by approximately 450 
pcm, and limits using the batch approach for online reprocessing simulations. 
Overall, the effective multiplication factor gradually decreases from 1.075 to 
$\approx$1.02 at equilibrium after approximately 6 years of irradiation.

@@

normalized power distribution of the \gls{MSBR} quarter core for equilibrium fuel
 salt composition. For both the initial and equilibrium compositions, fission 

@@

during reactor operation results in slightly different power fractions at startup and 
equilibrium, but most of the power is still generated in zone I at equilibrium 
(table~\ref{tab:powgen_fraction}. 

@@

generated in zone I.

@@

The average thorium feed rate increases during the first 500 days of operation, 
and steadily decreases due to spectrum hardening and accumulation of 
absorbers in the core. As a result, the average $^{232}$Th feed rate over 60 
years of operation is about 2.40 kg/day. This thorium consumption rate is in 
good agreement with a recent online reprocessing study by \gls{ORNL} 
\cite{betzler_molten_2017}.

>>>>

Additionally, the presence of rubidium, strontium, cesium, and barium in the 
core are disadvantageous to reactor physics. In fact, the removal of these elements 
every 3435 days causes the multiplication factor to jump by approximately 450 
pcm, and limits using the batch approach for online reprocessing simulations. 
In future versions of SaltProc this drawback will be eliminated by removing 
elements with longer residence times (seminoble metals, volatile fluorides, Rb, Sr,
 Cs, Ba, Eu) using different approach. Only mass fraction (calculated 
 separately for each reprocessing group) will be removed every depletion step 
 (e.g. 3 days) instead of removing 100\% of element atoms after cycle time.
Overall, the effective multiplication factor gradually decreases from 1.075 to 
$\approx$1.02 at equilibrium after approximately 6 years of irradiation.

@@

normalized power distribution of the \gls{MSBR} quarter core, which is the same 
at both the initial and equilibrium states. For both the initial and equilibrium compositions, fission 

@@

during reactor operation results in different power fractions at startup and 
equilibrium, but most of the power is still generated in zone I at equilibrium. 

@@

generated in zone I and the majority of $^{233}$Th is 
produced in zone II.

@@

The average thorium feed rate increases during the first 500 days of operation, 
and steadily decreases due to spectrum hardening and accumulation of 
absorbers in the core. As a result, the average $^{232}$Th feed rate over 60 
years of operation is about 2.40 kg/day. This thorium consumption rate is in 
good agreement with a recent online reprocessing study by \gls{ORNL} 
\cite{betzler_molten_2017}. It must be noted that for the reactor with only 
thorium feed, at near equilibrium state, the thorium consumption rate is 
determined by the reactor power, the energy released per fission, and 
neutron energy spectrum.
